### 2021-03-23 Chapter-2/Chapter-2.tex
Updates from Overleaf

\section{Side-channel Attacks}
Address-based side-channel attacks happen when a program has different behaviors when it accesses different memory addresses. In many situations,  computer systems allow the attacker to shares some hardware resources (e.g., Cache, TLB, and DRAM) with the victim~\cite{ge2018survey,szefer2019survey}. As a result, an attacker can probe the shared hardware resource to infer the sensitive information. While the root reason of the attack is the same, there are various approaches that can exploit the attack at different granularities.

@@

Table~\ref{table:side_channel_attack} shows some representations of the recent side-channel attacks.

>>>>

\section{Side-channel Attacks}
Address-based side-channel attacks happen when a program accesses different memory addresses when it processes different secrets. In many situations, an attacker may shares some hardware resources (e.g., Cache, TLB, and DRAM) with the victim in today's computer system ~\cite{ge2018survey,szefer2019survey}. As a result, the attacker can probe the shared hardware resource to infer the sensitive information. While the root reason of the attack is the same, there are various approaches that can exploit the attack at different granularities.

@@

Table~\ref{table:side_channel_attack} shows some representations of the recent side-channel attacks. For a detailed overview of recent side-channel attacks, we refer to the following survey paper~\cite{ge2018survey}. We classified those side-channel attacks into two categories: cache channels and page channels.
